Multiscale Modeling of the Paradoxical Roles of the Immune System in EMT-Mediated Cancer

### 2019-02-25 Paper/Paper.tex
Next Par

\tcr{Still need to address Qing's comments on this paragraph.}
The tumor interacts with the immune system by initiating the sequence of events that results in the activation of the adaptive immune response.
It accomplishes this by presenting antigens that innate immune cells recognize and carry to lymph nodes to activate, among other things, T cells.
Also, tumor cells engage in certain cellular processes that shape the TME and thus impact the immune system.
In particular, tumor cells release transforming growth factor beta (TGF-$\beta$) that creates a tumor-supportive environment by shifting the immune balance to being immunosuppressive via enhancing activation of Treg cells.

@@

\tcr{Haven't addressed any of Qing's comments below this remark.}
The research on mesenchymal cells' immune evasiveness is quite conclusive with the research even going so far as establishing functional causes for this phenomenon.
As a cell is being targeted by cytotoxic immune cells for clearance, a physical connection between the two cells must be created in order to precipitate the lysing event.
This immunological synapse, however, is dependent upon the surface proteins of the target cell, and in the case of mesenchymal cells there is preliminary evidence that these surface markers are down-regulated in such a way that the immune synapse is more difficult to form\cite{terry2017new}.
There are also other structural changes that take place in mesenchymal cells that could contribute to this refractory nature towards immune clearance.
Regardless, the evidence currently demonstrates a ``slipperiness'' of mesenchymal cells in regards to immune lysing that in our model we will refer to as mesenchymal immune evasion, or MIE.

>>>>

\tcr{Still need to address Qing's comments on this paragraph:}

The tumor interacts with the immune system by initiating the sequence of events that results in the activation of the adaptive immune response.
It accomplishes this by presenting antigens that innate immune cells recognize and carry to lymph nodes to activate, among other things, T cells.
Also, tumor cells engage in certain cellular processes that shape the TME and thus impact the immune system.
In particular, tumor cells release transforming growth factor beta (TGF-$\beta$) that creates a tumor-supportive environment by shifting the immune balance to being immunosuppressive via enhancing activation of Treg cells.

@@

The immune evasiveness of mesenchymal cells is well-established with even a functional cause for this phenomenon.
As a cell is being targeted by cytotoxic immune cells for clearance, a physical connection between the two cells must be created in order to precipitate the lysing event.
This immunological synapse, however, is dependent upon the surface proteins of the target cell, and in the case of mesenchymal cells there is preliminary evidence that these surface markers are down-regulated in such a way that the immune synapse is more difficult to form\cite{terry2017new}.
There are also other structural changes that take place in mesenchymal cells that could contribute to this refractory nature towards immune clearance.
Regardless, the evidence currently demonstrates a ``slipperiness'' of mesenchymal cells in regards to immune lysing.
We will refer to this as mesenchymal immune evasion, or MIE.

\tcr{Haven't addressed any of Qing's comments below this remark.}
